\mytitile\\~

### 2019-10-29 document.tex
AppenB and results

Now, the complete Hamiltonian of SAM contains two terms describing each of them in isolation (with the corresponding annihilation operators $\hat b$ and $\hat c$, the $ge$ frequencies $\omega_{1,2}$ and anharmonicities $\alpha_{1,2}$), two terms representing the interaction of each transmon with the driving field at the same frequency $\omega_d$, and the transmon-transmon interaction term:
\begin{equation}\label{Hsystem}
\hat H = \hat H_{tr1}+\hat H_{tr2}+\hat H_{dr1}+\hat H_{dr2}+\hat H_{int},
\end{equation}
where $\hat H_{int} = J (\hat b +\hat b^\dag)(\hat c+\hat c^{\dagger})$ is the transverse interaction between the atoms. In the following, we will also transform \eqref{eq:master} into the frame rotating with both drives by an operator
\begin{align}
&\hat R = \exp[-i t (\omega_d^1 b^{\dagger}b+\omega_d^2 c^{\dagger}c)],\\
&\hat H_R = \hat R^{\dagger}\hat H \hat R - i\hat R^{\dagger}\partial_t \hat R.
\end{align}
After the transformation and application of RWA:
\begin{equation}
\begin{aligned}
	\omega_{(1,2)} &\rightarrow \Delta_{(1,2)} = \omega_d^{(1,2)}-\omega_{(1,2)},\\
	\hat H_{int} &\rightarrow J \left[\hat b^\dag \hat c e^{(\omega_d^1 - \omega_d^2)t} + \hat b \hat c^\dag e^{-(\omega_d^1 - \omega_d^2)t}\right],\\
	\hat H_{dr}^1 &\rightarrow \frac{\Omega_1}{2}(\hat b  + \hat b^\dag),\\ 
	\hat H_{dr}^2 &\rightarrow \frac{\Omega_2}{2}(\hat c  + \hat c^\dag).
\end{aligned}
\label{eq:RWA}
\end{equation}

@@

The readout resonator is not included in the model since in the dispersive regime is does not affect the dynamics of the SAM. Hence, the readout is modelled just by using the measurement operator $\hat M(f_p)$ that can be obtained by measuring the transmission $S_{21}(f_p)$ ($f_p$ is the probe frequency near the resonance) through the sample for the nine different states of the SAM $\ket{ij},\ i=0..2,\ j=0..2$\cite{filipp2009two}. Another way to find $\hat M(f_p)$ is to calculate the transmission by offsetting the experimental resonance curve using the dispersive shifts corresponding to these states. Since we have not directly measured the dispersive shifts, in our modelling they are treated as fitting parameters. Finally, the observable value for any state $\hat \rho$ is calculated as $S_{21}^{sim}(f_p) = \Tr[\hat M(f_p) \hat \rho]$.

@@

The second mode is required when it is not possible to avoid the time-dependence of the Liouvillian. This is the case when the transmons have to be excited at different frequencies ($\omega_d^1 - \omega_d^2 = \delta \neq 0$). From \eqref{eq:RWA} we find that even in the doubly-rotating frame $\hat H_{int}$ is oscillating, and it is not possible to simply drop this term in RWA because this will lead to qualitatively different results. In this case, to find the steady state of the system we employ the qutip's \textit{propagator} and \textit{propagator\_steadystate} functions. The propagator is a completely positive map $\Lambda(t_1, t_0): \hat \rho(t_0) \rightarrow \hat \rho(t_1)$ describing the time evolution of the system density matrix; for \eqref{eq:master}, it is defined as
\begin{equation}
\Lambda(t_1, t_0) = \mathcal{T} \exp [\int_{t_0}^{t_1} \mathcal L(\tau) d\tau],
\label{eq:propagator}
\end{equation}
where $\mathcal T$ is the time-ordering superoperator. Since the Liouvillian is periodic with a period of $T = 2\pi/\delta$, it is possible to calculate the steady state as the eigenvector $\hat \rho_{ss}$ of the single-period propagator $\Lambda(T, 0)$ corresponding to its largest eigenvalue\cite{dittrich1998quantum, rivas2012open}. Upon infinite applications of $\Lambda$: 
\[
\lim_{n\to \infty} \left[\Lambda(T, 0)\right]^n \hat \rho = \Lambda(nT, 0) \hat \rho \to \hat \rho_{ss}.
\]

@@

\subsection{\label{sec:level1} Spectroscopy: experiment and numerical simulation}

@@

	\centering
	\includegraphics[width=\linewidth]{main_picture}
	\caption{Two-tone spectroscopy: experiment \textbf{(a)} and numerical modelling \textbf{(b)}. Colour shows the real part of complex transmission  through the sample. Two transmons are aligned as in \autoref{fig:experiment}~(c) and thus the picture is symmetric. Panel \textbf{(a)} contains an additional horizontal line which origins from a parasitic resonance interacting with the readout resonator but not with the SAM. Three avoided crossings not predicted by the stationary model are shown in insets I, II and III; some other pronounced features reproduced by the modelling are shown with numbered markers (see text for description). In panel \textbf{(b)}, we also denote where possible some of the transitions $\ket{00}\rightarrow \ket{ij/n}$ where $i,j$ stand for the transmon eigenstates and $/n$ is optional for an $n$-photon process.}
	\label{fig:two-tone}
\end{figure*}

Experiment was conducted as described in Appendix \ref{sec:meas_setup}. We have used high-power two-tone spectroscopy (qubit Rabi frequencies $\Omega_1$ and $\Omega_2$ were around 20 MHz) to probe transitions between eigenstates of our SAM; the result is shown in \autoref{fig:two-tone}~(a). As one can see, several spectral lines are visible besides the $ge$ ones shown in \autoref{fig:experiment}~(c). Their frequency depends on the applied current, and at multiple points they become resonant with each other. At three pairs of these resonant points, we observe three distinct features shown in insets marked with Roman numerals. Some secondary details are shown with Arabic-numbered markers.

Remarkably, in areas I, II and III we could observe avoided crossings which turn out to be impossible to explain using only the stationary Hamiltonian without driving terms. We confirm this by numerically diagonalizing it taking 3 levels for each transmon (and total 9 states of SAM); all possible transitions between all eigenlevels of the SAM are shown in \autoref{fig:statinary_levels} in Appendix. While correctly reproducing, for instance, the avoided crossing labelled as feature 3 in \autoref{fig:two-tone}, it completely misses the Roman-numbered effects. Taking into account more energy levels of each transmon does not help, and is not even necessary to reproduce this effect, as we will show below.

To check whether these avoided crossings are observable in the dynamic regime, we have solved the master equation \eqref{eq:master} to find the steady state of the system $\hat \rho_{ss}$ and the corresponding expected measurement outcome $\mathfrak{Re}\left[\Tr[\hat M \hat \rho_{ss}]\right]$. Strikingly, all the experimental features are immediately reproduced using this approach even with only 9 SAM states. We have solved \eqref{eq:master} with and without RWA (using the propagator approach \eqref{eq:propagator}) and did not find any noticeable difference in the result; though, the runtime of a single 401 by 401 points simulation was 9 hours without RWA vs. 3 minutes with RWA.

Next, we have focused on the feature III and have reproduced this avoided crossing in an additional numerical simulation taking only 2 levels for the transmon 1 and three levels for the other (not shown, should we show?). Upon this, it has become clear that feature II and feature III actually have the same nature and differ only by the ordering of the transmons: for II, they appear whence the transition from $\ket{00}$ to $\ket{01}$ intersects with a two-photon one to $\ket{20/2}$ ($\ket{10}$ intersects $\ket{02/2}$ in III); one can see this clearly in \autoref{fig:two-tone}~(b) where the spectral lines are identified with the corresponding transitions.

All of the observed features depend significantly on power.

@@

\begin{figure*}
	\centering
	\includegraphics[width=\linewidth]{drawing}
	\caption{Drive acts on the one of qubit, with different amplitude 100,200,300 MHz}
	\label{fig:difdrive}
\end{figure*}

@@

\renewcommand{\kbldelim}{[}% Left delimiter
\renewcommand{\kbrdelim}{]}% Right delimiter
\begin{widetext}
	\begin{equation}\label{matrix} 
	\text{$H^R$} = \kbordermatrix{
	&\ket{00} & \ket{10} & \ket{01} & \ket{11} & \ket{02} & \ket{12} \\
	\ket{00}& 0 & \text{$\Omega_1/2 $} & \text{$\Omega _2$} e^{i \text{$\delta_{\omega}$} t}/2 & 0 & 0 & 0 \\
	\ket{10} & \text{$\Omega_1/2 $} & \text{$-\Delta_1 $} & J & \text{$\Omega_2$} e^{i \text{$\delta_{\omega}$} t}/2 & 0 & 0 \\
	\ket{01} & \text{$\Omega_2$} e^{-i \text{$\delta_{\omega} $} t}/2 & J & -\text{$\Delta_2 $} &
	\text{$\Omega_1$/2} & \sqrt{2} \text{$\Omega_2$} e^{i \text{$\delta_{\omega}$} t}/2 & 0 \\
	\ket{11} & 0 & \text{$\Omega_2$} e^{-i \text{$\delta_{\omega} $} t}/2 & \text{$\Omega_1/2$} &
	\text{$-\Delta_2 -\Delta_1$} & \sqrt{2} J & \sqrt{2} \text{$\Omega_2$} e^{i \text{$\delta_{\omega}
			$} t}/2 \\
	\ket{02} & 0 & 0 & \sqrt{2} \text{$\Omega_2$} e^{-i \text{$\delta_{\omega}$} t}/2 & \sqrt{2} J &
	\text{$\alpha$}-2 \text{$\Delta_2$} & \text{$\Omega_1/2$} \\
	\ket{12} & 0 & 0 & 0 & \sqrt{2} \text{$\Omega_2$} e^{-i \text{$\delta_{\omega} $} t}/2 & \text{$\Omega_1/2
		$} & \text{$\alpha$}-2 \text{$\Delta_2$}- \text{$\Delta_1$} \\
}
	\end{equation}
\end{widetext}
Where $\Omega_1$, $\Omega_2$ - amplitudes of the drives, $\Delta_1 = \omega_d-\omega_{tr1}=0$,$\Delta_2 = \omega_d-\omega_{tr2}$.
Let's consider the Hamiltonian (\autoref{matrix}) in details. Divide it into three parts: time-dependent $(V_t)$, the part responsible for the interaction between the qubits $(V_J)$ and all the rest $(H_0)$.
\begin{equation}
	H^R=H_0+V_J+V_t
\end{equation}
The $\Omega_1\gg \Omega_2,\Delta_2\gg J$, so the driven field on the first qubit is strong and form the dressed states defined by the Hamiltonian $H_0$.
The Hamiltonian $H_0$ is station and we can find eigenvectors and eigenvalues. The drive on the second qubit is weak with very low intensity, so we can neglect any perturbation introduced by second drive on the position, width os the dressed states.
Firstly, we consider the system of non-interacting qubits $(J=0)$. In this case some transitions are prohibited and the splitting we are interested in is not observed. 
Therefore a non-zero interaction between qubits is necessary to observe AT effect.

After that according to the perturbation theory (with perturbation $V_J$) to $H_0$ we found the first-order corrections to the wave functions. We can use Fermi Golden Rule to find the probability of transition.
\appendix

@@

\section{Theoretical description of two-photon process}
Perturbation theory allows semianalytical calculation of the transition rates (Rabi oscillation frequencies) for single and multi-photon processes.

Let's consider the Hamiltonian $H = H_0+V(t)$, with time-dependent interaction $V(t)$ and "reference" part -- $H_0$ and wave function $\Psi(t)$. After switching to the interaction picture $V(t)$ modifies to $\tilde{V}(t) = \exp(i H_0 t)V(t)\exp(-i H_0 t)$ and Schrödinger equation gives by $i \derivative{\psi(t)}{t}=\tilde{V}(t)\psi(t)$, where $\psi(t)=\exp(i H_0 t)\Psi(t)$. The reference states of $H_0$ will be denoted $\ket{j}$, $H_0 \ket{j} = \omega_j \ket{j}$ whence it follows that matrix elements  of the modified interaction take the form $\bra{j}\tilde{V}(t)\ket{i}=\exp(i(\omega_j-\omega_i)t)\bra{j}V(t)\ket{i}$. A "solution" of Schrödinger equation in interaction picture corresponding to the initial reference state $\ket{i}$ is
\begin{equation}\label{forpsi}
	\psi_i(t)=\ket{i} - i \int_{-\infty}^{t}dt_1\tilde{V}(t_1)\ket{\psi_i(t_1)}
\end{equation}

The quantity of primary interest is not the wave function but the probability of transition from the initial state $\ket{i}\rightarrow\ket{f}$, where $\ket{f}$ is the final state of interest. Firstly, we find the transition amplitude $A_{fi} = \bra{f}U(t,t_0)\ket{i}=\bra{f}\psi_i(t)$ where $U(t,t_0)$ evolution operator.

Solving \autoref{forpsi} by simple iteration gives the series solution
\begin{equation}
	U(t,t_0) = 1+\sum_{n}U^{(n)}(t,t_0)
\end{equation}
\begin{equation}
	U^{(n)}(t,t_0) = -i^n \int_{t_0}^{t}d t_1\tilde{V}(t_1)...\int_{t_0}^{t_{n-1}}d t_n\tilde{V}(t_n)
\end{equation}
For "weak" interaction the series may be truncated to a fine term $n$ and the $n$th- order transition amplitude $\bra{f}U^{(n)}(t,t_0)\ket{i}$ can be evaluated. 
In our case the interaction in interaction picture satisfies the following relation
\begin{equation}
	\begin{split}
	\tilde{V}(t)=\exp(i H_0 t) \Omega\cos(\omega_d t)(\hat b+\hat b^{\dagger})\exp(-i H_0 t)\overset{RWA}{=}\\ \exp(i H_0 t) \Omega(\hat b^{\dagger} e^{-i\omega_d t}+\hat be^{i\omega_d t})\exp(-i H_0 t)
	\end{split}
\end{equation}
Taking the matrix element between the initial and the final states $\ket{i}$ and $\ket{f}$, one immediately obtains
\begin{equation}
	\begin{split}
	\bra{f}U^{(1)}(t,t_0)\ket{i}=-i\int_{t_0}^{t}dt_1\tilde{V}(t_1)=\\-i\frac{\Omega}{2}\big[\int_{t_0}^{t}dt_1e^{i(\omega_f-\omega_i-\omega_d)t_1}\bra{f}b^{\dagger}\ket{i}+\\
	\int_{t_0}^{t}dt_1e^{i(\omega_f-\omega_i+\omega_d)t_1}\bra{f}b\ket{i}\big]
	\end{split}
\end{equation}
To calculate second-order term we used the following expression $\sum_{j}\ket{j}\bra{j}=\mathbbm{1}$.
\begin{equation}
	\begin{split}
	\bra{f}U^{(2)}(t,t_0)\ket{i}=-\bra{f}\int_{t_0}^{t}dt_1\tilde{V}(t_1)\mathbbm{1}\int_{t_0}^{t_1}dt_2\tilde{V}(t_2)\ket{i}=\\-\int_{t_0}^{t}dt_1 e^{i(\omega_f-\omega_j)t_1}\bra{f}V(t_1)\ket{j}\int_{t_0}^{t_1}dt_2e^{i(\omega_j-\omega_i)t_2}\bra{j}V(t_2)\ket{i}
	\end{split}
\end{equation}
Go over the long-time limit $t\rightarrow\infty$ in the final integral and collect the terms belongings to the same delta functions. This gives
\begin{equation}
	\begin{split}
	\bra{f}U^{(2)}(\infty)\ket{i}=\\\frac{\pi i\Omega^2}{2}\bigg[\delta(\omega_f-\omega_i+2\omega_d)\sum_j\frac{\bra{f}b\ket{j}\bra{j}b\ket{i}}{\omega_j-\omega_i+\omega_d}+\\
	\delta(\omega_f-\omega_i)\bigg(\sum_j\frac{\bra{f}b^{\dagger}\ket{j}\bra{j}b\ket{i}}{\omega_j-\omega_i+\omega_d}+\\
	\sum_j\frac{\bra{f}b\ket{j}\bra{j}b^{\dagger}\ket{i}}{\omega_j-\omega_i-\omega_d}\bigg)+\\
	\delta(\omega_f-\omega_i-2\omega_d)\sum_j\frac{\bra{f}b^{\dagger}\ket{j}\bra{j}b^{\dagger}\ket{i}}{\omega_j-\omega_i-\omega_d}\bigg]
	\end{split}
\end{equation}

\section{Measurement setup and methods}\label{sec:meas_setup}
The sample was measured in a BlueFors LD250 dilution refrigerator at 16 mK. For the readout a Keysight PNA-L N5232A VNA was used. For the coherent excitation of the SAM, we used an Agilent MXG N5183B analog signal generator. The sample was 
flux biased using Yokogawa GS200 current sources (two for the flux lines and one for the external coil wrapped around the sample).

Input microwave lines were isolated from high-temperature noise with 60 dB of attenuation (10 @ 4K, 10 @ 1K, 20 @ 100 and 16 mK) and custom-made IR filters. The additional on-chip attenuation (due to the small capacitive coupling) between the qubit drive line and the qubits was calculated in Sonnet to be around 70 dB @ 6 GHz. Coaxial flux-bias lines were attenuated by 20 dB @ 4K and IR filtered as well. Output path contained two 20 dB isolators and two amplifiers: the 4-14 GHz LNF amplifier at the 4 K stage and the room-temperature LNF amplifier.

As the main experimental method, we have employed the two-tone spectroscopy which consists of exciting the SAM with monochromatic light at certain frequency until steady state is reached while simultaneously measuring the signal transmission at the readout resonator frequency. This measurement yields the average value of the joint measurement operator $\hat M$ in the steady-state.

>>>>

Now, the complete Hamiltonian of SAM contains two terms describing each of them in isolation (with the corresponding annihilation operators $\hat b$ and $\hat c$ and the $ge$ frequencies $\omega_{1,2}$), two terms representing the interaction of each transmon with the driving field at the same frequency $\omega_d$, and the transmon-transmon interaction term:
\begin{equation}\label{Hsystem}
\hat H = \hat H_{tr1}+\hat H_{tr2}+\hat H_{dr1}+\hat H_{dr2}+\hat H_{int},
\end{equation}
where $\hat H_{int} = J (\hat b +\hat b^\dag)(\hat c+\hat c^{\dagger})$ is the transverse interaction between the atoms. In the following, we will also transform \eqref{eq:master} into the frame rotating with both drives by an operator
\begin{align}
&\hat R = \exp[i (\omega_d^1 b^{\dagger}b+\omega_d^2 c^{\dagger}c)t],\\
&\hat H_R = \hat R^{\dagger}\hat H \hat R + i\hat R^{\dagger}\partial_t \hat R.
\end{align}
After the transformation and application of RWA:
\begin{equation}
\begin{aligned}
	\omega_{(1,2)} &\rightarrow \Delta_{(1,2)} = \omega_{(1,2)} - \omega_d^{(1,2)},\\
	\hat H_{int} &\rightarrow J \left[\hat b^\dag \hat c e^{-(\omega_d^1 - \omega_d^2)t} + \hat b \hat c^\dag e^{(\omega_d^1 - \omega_d^2)t}\right],\\
	\hat H_{dr}^1 &\rightarrow \frac{\Omega_1}{2}(\hat b  + \hat b^\dag),\\ 
	\hat H_{dr}^2 &\rightarrow \frac{\Omega_2}{2}(\hat c  + \hat c^\dag).
\end{aligned}
\label{eq:RWA}
\end{equation}

@@

The readout resonator is not included in the model since in the dispersive regime is does not affect the dynamics of the SAM. The readout is modelled just by using the measurement operator $\hat M(f_p)$ that can be obtained by measuring the transmission $S_{21}(f_p)$ ($f_p$ is the probe frequency near the resonance) through the sample for the nine different states of the SAM $\ket{ij},\ i=0..2,\ j=0..2$\cite{filipp2009two}. Another way to find $\hat M(f_p)$ is to calculate the transmission using the dispersive shifts for these states by correspondingly offsetting the experimental resonance curve. Since we have not directly measured the dispersive shifts, in our modelling they are treated as fitting parameters. Finally, the observable value for any state $\hat \rho$ is calculated as $S_{21}^{sim}(f_p) = \Tr[\hat M(f_p) \hat \rho]$.

@@

The second mode is required when it is not possible to avoid the time-dependence of the Liouvillian. This is the case when the transmons have to be excited at different frequencies ($\omega_d^1 - \omega_d^2 = \delta \neq 0$). From \eqref{eq:RWA} we find that even in the doubly-rotating frame $\hat H_{int}$ is oscillating, and it is not possible to simply drop this term in RWA because this will lead to qualitatively different results. In this case, to find the steady state of the system we employ the qutip's \textit{propagator} and \textit{propagator\_steadystate} functions. The propagator is a completely positive map $\Lambda(t_1, t_0): \hat \rho(t_0) \rightarrow \hat \rho(t_1)$ describing the time evolution of the system density matrix; for \eqref{eq:master}, it is defined as
\begin{equation}
\Lambda(t_1, t_0) = \mathcal{T} \exp [\int_{t_0}^{t_1} \mathcal L(\tau) d\tau],
\end{equation}
where $\mathcal T$ is the time-ordering superoperator. Since the Liouvillian is periodic with a period of $T = 2\pi/\delta$, it is possible to calculate the steady state as the eigenvector $\hat \rho_{ss}$ of the single-period propagator $\Lambda(T, 0)$ corresponding to its largest eigenvalue\cite{dittrich1998quantum, rivas2012open}. Upon infinite applications of $\Lambda$: 
\[
\lim_{n\to \infty} \left[\Lambda(T, 0)\right]^n \hat \rho = \Lambda(nT, 0) \hat \rho \to \hat \rho_{ss}.
\]

@@

\subsection{\label{sec:level1} Experimental and numerical parts}

Two tone spectroscopy was found experimentally and shows good agreement with modelling data \autoref{fig:two-tone}.

@@

	\centering
	\includegraphics[width=\linewidth]{main_picture}
	\caption{Two-tone spectroscopy: (a) Experiment;b(b) Modelling ; the colorbar is common.  Clear flux-dependent transmon transitions are visible.}
	\label{fig:two-tone}
\end{figure*}

@@

We obtain illustrative example of dressed states\autoref{fig:difdrive}. On this figure the microwave drive acts only on the one of qubits. 
\begin{figure*}
	\centering
	\includegraphics[width=\linewidth]{drawing}
	\caption{Drive acts on the one of qubit, with different amplitude 100,200,300 MHz}
	\label{fig:difdrive}
\end{figure*}

@@

\renewcommand{\kbldelim}{[}% Left delimiter
\renewcommand{\kbrdelim}{]}% Right delimiter
\begin{widetext}
	\begin{equation}\label{matrix} 
	\text{$H^R$} = \kbordermatrix{
	&\ket{00} & \ket{10} & \ket{01} & \ket{11} & \ket{02} & \ket{12} \\
	\ket{00}& 0 & \text{$\Omega_1/2 $} & \text{$\Omega _2$} e^{i \text{$\delta_{\omega}$} t}/2 & 0 & 0 & 0 \\
	\ket{10} & \text{$\Omega_1/2 $} & \text{$-\Delta_1 $} & J & \text{$\Omega_2$} e^{i \text{$\delta_{\omega}$} t}/2 & 0 & 0 \\
	\ket{01} & \text{$\Omega_2$} e^{-i \text{$\delta_{\omega} $} t}/2 & J & -\text{$\Delta_2 $} &
	\text{$\Omega_1$/2} & \sqrt{2} \text{$\Omega_2$} e^{i \text{$\delta_{\omega}$} t}/2 & 0 \\
	\ket{11} & 0 & \text{$\Omega_2$} e^{-i \text{$\delta_{\omega} $} t}/2 & \text{$\Omega_1/2$} &
	\text{$-\Delta_2 -\Delta_1$} & \sqrt{2} J & \sqrt{2} \text{$\Omega_2$} e^{i \text{$\delta_{\omega}
			$} t}/2 \\
	\ket{02} & 0 & 0 & \sqrt{2} \text{$\Omega_2$} e^{-i \text{$\delta_{\omega}$} t}/2 & \sqrt{2} J &
	\text{$\alpha$}-2 \text{$\Delta_2$} & \text{$\Omega_1/2$} \\
	\ket{12} & 0 & 0 & 0 & \sqrt{2} \text{$\Omega_2$} e^{-i \text{$\delta_{\omega} $} t}/2 & \text{$\Omega_1/2
		$} & \text{$\alpha$}-2 \text{$\Delta_2$}- \text{$\Delta_1$} \\
}
	\end{equation}
\end{widetext}
Where $\Omega_1$, $\Omega_2$ - amplitudes of the drives, $\Delta_1 = \omega_d-\omega_{1}=0$,$\Delta_2 = \omega_d-\omega_{2}$, $\delta_{\omega} = \omega_{dr1}-\omega_{dr2}$.
Let's consider the Hamiltonian (\autoref{matrix}) in details. Divide it into three parts: time-dependent $(V_t)$, the part responsible for the interaction between the qubits $(V_J)$ and all the rest $(H_0)$.
\begin{equation}
	H^R=H_0+V_J+V_t
\end{equation}
The $\Omega_1\gg \Omega_2,\Delta_2> J$, so the driven field on the first qubit is strong and form the dressed states defined by the Hamiltonian $H_0$, which is stationary, so the levels can be found and schematically depicted in \autoref{fig:main_scheme}~(b). The drive on the second qubit is weak with very low intensity, so we can neglect any perturbation introduced by second drive on the position, width of the dressed states.
At our working point the condition $\Delta_2=\alpha/2$ is met and $H_0$ becomes degenerate.

According to the degenerate perturbation theory (with perturbation $V_J$) we found the first-order corrections to the wave functions. Calculating the probability of two-photon transition per unit interaction time using the \autoref{prob} for corrected  wave functions and neglecting small terms we obtain:
\begin{equation}
	A^{(2)}_{1\rightarrow 6} =\frac{\pi\Omega_2^4}{8} \frac{8 J^4 (6 \text{$\alpha $}+19 \text{$\Omega_1 $})^2}{\text{$\alpha
			$}^6 \text{$\Omega_1$}^2}
\end{equation}
\begin{equation}
A^{(2)}_{2\rightarrow 5} =\frac{\pi\Omega_2^4}{8} \frac{8 J^4 (6 \text{$\alpha $}-19 \text{$\Omega_1 $})^2}{\text{$\alpha
		$}^6 \text{$\Omega_1$}^2}
\end{equation}

So, in the system of non-interacting qubits $(J=0)$ some transitions are prohibited and the splitting we are interested in is not observed. Therefore a non-zero interaction between qubits is necessary to observe AT effect in our system.

\appendix

@@

\section{Degenerate perturbation theory}
\begin{equation}
H^R=H_0+V_J
\end{equation}
At our working point the equation $\Delta_2=\alpha/2$ is true and $H_0$ becomes degenerate. Let's consider our system in the basis of dressed states.
\begin{equation}
H_0^{d}= diag(-\frac{\Omega_{1}}{2},\frac{\Omega_{1}}{2},\frac{(-\alpha-\Omega_{1})}{2},\frac{-\alpha+\Omega_{1}}{2},-\frac{\Omega_{1}}{2},\frac{\Omega_{1}}{2})
\end{equation}
The choice of wave functions from a degenerate subspace is arbitrary because any linear combination of functions from this subspace will satisfy the Schrodinger equation. However, if we demand that the change of wave functions be small under the applied small perturbation, then the choice of wave functions become defined. To obtain correct wave functions we need to diagonalize $V_J^{d}$ in the degenerate subspace. However, we can notice that $V_J^{d}$ is identically the zero matrix in our subspace, so technically any choice of basis will diagonalize $V_J^{d}$. This means that the degeneracy is not lifted at first-order in perturbation theory. We have to pick eigenvectors which diagonalize following matrix:
\begin{equation}
	\begin{matrix}
	M_{nn'} = \sum_{m}\frac{V_{nm}V_{mn'}}{E_n-E_m}
	\end{matrix}
\end{equation}
Where $\ket{n}$ and $\ket{n'}$ are states with same energy $E_n$.  The sum is over all states $m$ not in the degenerate subspace.
For example, in our case for one of degenerate subspaces:
\begin{equation}
	M_{15} =\left[\begin{matrix}\frac{J^{2} \left(\Omega_{1} - \alpha\right)}{\alpha \left(2 \Omega_{1} - \alpha\right)} & \frac{\sqrt{2} J^{2} \Omega_{1}}{\alpha \left(2 \Omega_{1} - \alpha\right)}\\\frac{\sqrt{2} J^{2} \Omega_{1}}{\alpha \left(2 \Omega_{1} - \alpha\right)} & \frac{2 J^{2} \left(\Omega_{1} - \alpha\right)}{\alpha \left(2 \Omega_{1} - \alpha\right)}\end{matrix}\right]
\end{equation}
The normalized eigenvectors $(C_n,C_{n'})$ of the matrix will give the desired zero approximation wave-functions.
The first-order correction to the states from degenerate subspace:
\begin{equation}
	\ket{n^0}+\ket{n^1} = \sum_n C_{n}\ket{n^0} + \sum_{m\ne n}\ket{m^0}\frac{\bra{m^0}V\ket{n^0}}{E_n^0-E_m^0}
\end{equation}
The sum is over all states $n$ in the degenerate subspace $n=(n,n')$.
The first-order corrections for not degenerate state compute by using the ordinary perturbation theory.
\begin{equation}
	\ket{j^1} = \sum_{m\ne j}\ket{m^0}\frac{\bra{m^0}V\ket{j^0}}{E_j^0-E_m^0}
\end{equation}

\section{Theoretical description of two-photon process}
Perturbation theory allows semianalytical calculation of the transition rates for single and multi-photon processes\cite{faisal2013theory}.

Let's consider the Hamiltonian $H = H_0+V(t)$, with time-dependent interaction $V(t)$ and "reference" part -- $H_0$. After switching to the interaction picture $V(t)$ modifies to $\tilde{V}(t) = \exp(i H_0 t)V(t)\exp(-i H_0 t)$ and Schrödinger equation gives by $i \derivative{\tilde{\psi}(t)}{t}=\tilde{V}(t)\tilde{\psi}(t)$. The reference states of $H_0$ will be denoted as $\ket{j}$, $H_0 \ket{j} = \omega_j \ket{j}$ whence it follows that matrix elements  of the modified interaction take the form $\bra{j}\tilde{V}(t)\ket{i}=\exp(i(\omega_j-\omega_i)t)\bra{j}V(t)\ket{i}$. A "solution" of Schrödinger equation in interaction picture corresponding to the initial reference state $\ket{i}$ is
\begin{equation}\label{forpsi}
	\tilde{\psi_i}(t)=\ket{i} - i \int_{-\infty}^{t}dt_1\tilde{V}(t_1)\ket{\tilde{\psi_i}(t_1)}
\end{equation}

Mainly important for us is to find not the wave function but the probability of transition from the initial state $\ket{i}\rightarrow\ket{f}$, where $\ket{f}$ is the final state. Firstly, we find the transition amplitude $A_{fi} = \bra{f}U(t,t_0)\ket{i}=\bra{f}\psi_i(t)$ where $U(t,t_0)$ evolution operator.

Solving \autoref{forpsi} by simple iteration gives the series solution
\begin{equation}
	U(t,t_0) = 1+\sum_{n}U^{(n)}(t,t_0)
\end{equation}
\begin{equation}
	U^{(n)}(t,t_0) = -i^n \int_{t_0}^{t}d t_1\tilde{V}(t_1)...\int_{t_0}^{t_{n-1}}d t_n\tilde{V}(t_n)
\end{equation}
For "weak" interaction the series may be truncated to a fine term $n$ and the $n$th- order transition amplitude $\bra{f}U^{(n)}(t,t_0)\ket{i}$ can be evaluated. 
In our case the interaction in interaction picture satisfies the following relation
\begin{equation}
	\begin{split}
	\tilde{V}(t)=\exp(i H_0 t) \Omega\cos(\omega_d t)(\hat b+\hat b^{\dagger})\exp(-i H_0 t)\overset{RWA}{=}\\ \exp(i H_0 t) \Omega(\hat b^{\dagger} e^{-i\omega_d t}+\hat be^{i\omega_d t})\exp(-i H_0 t)
	\end{split}
\end{equation}
Taking the matrix element between the initial and the final states $\ket{i}$ and $\ket{f}$, one immediately obtains
\begin{equation}
	\begin{split}
	\bra{f}U^{(1)}(t,t_0)\ket{i}=-i\int_{t_0}^{t}dt_1\tilde{V}(t_1)=\\-i\frac{\Omega}{2}\big[\int_{t_0}^{t}dt_1e^{i(\omega_f-\omega_i-\omega_d)t_1}\bra{f}b^{\dagger}\ket{i}+\\
	\int_{t_0}^{t}dt_1e^{i(\omega_f-\omega_i+\omega_d)t_1}\bra{f}b\ket{i}\big]
	\end{split}
\end{equation}
To calculate second-order term we used the following expression $\sum_{j}\ket{j}\bra{j}=\mathbbm{1}$.
\begin{equation}
	\begin{split}
	\bra{f}U^{(2)}(t,t_0)\ket{i}=-\bra{f}\int_{t_0}^{t}dt_1\tilde{V}(t_1)\mathbbm{1}\int_{t_0}^{t_1}dt_2\tilde{V}(t_2)\ket{i}=\\-\int_{t_0}^{t}dt_1 e^{i(\omega_f-\omega_j)t_1}\bra{f}V(t_1)\ket{j}\int_{t_0}^{t_1}dt_2e^{i(\omega_j-\omega_i)t_2}\bra{j}V(t_2)\ket{i}
	\end{split}
\end{equation}
Go over the long-time limit $t\rightarrow\infty$ in the final integral and collect the terms belongings to the same delta functions. This gives
\begin{equation}
	\begin{split}
	\bra{f}U^{(2)}(\infty)\ket{i}=\\\frac{\pi i\Omega^2}{2}\bigg[\delta(\omega_f-\omega_i+2\omega_d)\sum_j\frac{\bra{f}b\ket{j}\bra{j}b\ket{i}}{\omega_j-\omega_i+\omega_d}+\\
	\delta(\omega_f-\omega_i)\bigg(\sum_j\frac{\bra{f}b^{\dagger}\ket{j}\bra{j}b\ket{i}}{\omega_j-\omega_i+\omega_d}+\\
	\sum_j\frac{\bra{f}b\ket{j}\bra{j}b^{\dagger}\ket{i}}{\omega_j-\omega_i-\omega_d}\bigg)+\\
	\delta(\omega_f-\omega_i-2\omega_d)\sum_j\frac{\bra{f}b^{\dagger}\ket{j}\bra{j}b^{\dagger}\ket{i}}{\omega_j-\omega_i-\omega_d}\bigg]
	\end{split}
\end{equation}
The probability of two-photon transition from state $\ket{i}$ to state $\ket{f}$ is simply the square modulus of the corresponding amplitude. So, $P^{(2)}_{i\rightarrow f}= |	\bra{f}U^{(2)}(\infty)\ket{i}|^2$.
The rate (probability per unit interaction time T) of absorption of $2$ photons is defined as:
\begin{equation}
	W^{(2)}_{i\rightarrow f}=\lim\limits_{T\rightarrow\infty}\frac{P^{(2)}_{i\rightarrow f}}{T}
\end{equation}
For simplifier the equation we have made use of the relation:
\begin{equation}\nonumber
	\delta(\omega_f-\omega_i-2\omega_d) =\frac{1}{2\pi} \lim\limits_{T\rightarrow\infty}\int_{-T/2}^{T/2}e^{i(\omega_f-\omega_i-2\omega_d)t}dt = \lim\limits_{T\rightarrow\infty}\frac{T}{2\pi}
\end{equation} 
For $\omega_f=\omega_i+2\omega_d$.
\begin{equation}\label{prob}
\begin{split}
	W^{(2)}_{i\rightarrow f}=\frac{\pi\Omega^4}{8}\bigg|\sum_j\frac{\bra{f}b^{\dagger}\ket{j}\bra{j}b^{\dagger}\ket{i}}{\omega_j-\omega_i-\omega_d}\bigg|^2\delta(\omega_f-\omega_i-2\omega_d)=\\ A^{(2)}_{i\rightarrow f}\delta(\omega_f-\omega_i-2\omega_d)
\end{split}
\end{equation}
